How young children integrate information sources to infer the meaning of words

### 2021-05-18 paper/supplementary_material.Rmd
fix trial number in supplement
final submission

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of novel objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

```{r fig3, include = T,  fig.cap = "Proportion of choosing the object that was new to the speaker by age. Dots show the mean response for each participant. The solid black line shows the developmental trajectory based on the mean of the model posterior distribution. Lighter lines show 200 random draws from the posterior distribution to depict uncertainty. Dotted line indicates a level of performance expected by chance.", fig.width=12, fig.height = 4}
ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2))
```

@@

```{r bda, engine='tikz', echo = F , fig.cap = "Graphical model representing the Bayesian data analysis for **rational integration model** used for *Explanation*. $RSA$ represents the general model architecture and paremeters defined by Eq. \\@ref(eq:rsabasic1) - \\@ref(eq:rsabasic3). $L_1$ represents the RSA model defined by Eq. \\@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt. 1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt. 2).  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\\beta_0$ and $\\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $\\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}

@@

\resizebox{1\textwidth}{!}{

@@

}

@@

```{r fig4, include = T, fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
```

@@

```{r fig10, include = T, fig.cap = "Bias parameter for the biased model (A) and the developmental bias model (B). (A) shows the posterior distribution of the bias parameter and (B) shows developmental trajectories for the bias parameter based on 300 random draws from the posterior distribution for intercept and slope.", fig.width=10, fig.height = 4, }
ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1)
```

@@

```{r figa1, include = T, cache=F,  fig.cap = "Posterior distribution of intercept and slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 5}

@@

## Speaker informativeness and common ground sensitivity

>>>>

The general setup was the same as in Experiment 1. The speaker was positioned between the tables. There was a novel object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second novel object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1 (see also Figure \@ref(fig:fig1)B). The positioning of the novel object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced. Children received ten trials, each with a different pair of novel objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

```{r fig3, include = T,  fig.cap = "Proportion of choosing the object that was new to the speaker by age. Dots show the mean response for each participant. The solid black line shows the developmental trajectory based on the mean of the model posterior distribution. Lighter lines show 200 random draws from the posterior distribution to depict uncertainty. Dotted line indicates a level of performance expected by chance.", out.width="100%"}

#ggsave(plot = ggarrange(plot_cg, plot_comb,  labels = c("A","B"), nrow = 1, widths = c(1,2)), filename = "figures/figureS3.png", width = 12, height = 4)

knitr::include_graphics("figures/figureS3.png")
```

@@

(ref:bdalab) Graphical model representing the Bayesian data analysis for **rational integration model** used for *Explanation*. $RSA$ represents the general model architecture and paremeters defined by Eq. \@ref(eq:rsabasic1) - \@ref(eq:rsabasic3). $L_1$ represents the RSA model defined by Eq. \@ref(eq:rsafull1), used to predict the combination data $d^{Ex3}$ from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\alpha_i$ (which varies by age), a semantic knowledge parameter $\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{Ex1}$; Expt. 1), via the same RSA model with no common ground $L$; common ground sensitivity parameters $\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{Ex2}$; Expt. 2).  Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\mu$ and $\sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories.

```{r bda, engine='tikz', echo = F , fig.cap = "(ref:bdalab)", out.width = "100%"}

@@

@@

@@

```{r fig4, include = T, fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", out.width="100%"}

#ggsave(plot = ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1)), filename = "figures/figureS4.png", width = 12, height = 4)

knitr::include_graphics("figures/figureS4.png")
```

@@

```{r fig10, include = T, fig.cap = "Bias parameter for the biased model (A) and the developmental bias model (B). (A) shows the posterior distribution of the bias parameter and (B) shows developmental trajectories for the bias parameter based on 300 random draws from the posterior distribution for intercept and slope.", out.width="100%"}

#ggsave(plot = ggarrange(plot_mixture, plot_dev_mixture,  labels = c("A","B"), nrow = 1), filename = "figures/figureS10.png", width = 10, height = 4)

knitr::include_graphics("figures/figureS10.png")
```

@@

```{r figa1, include = T, cache=T,  fig.cap = "Posterior distribution of intercept and slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 5}

@@

## Speaker informativeness and sensitivity to common ground
